Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-26 wearables_survey.tex
un-roughed Questions section a bit

More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}. It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}. The demographics of wearables consumers are young and rich--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year. However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.

@@

\subsection{Threat Landscape Investigation} 
(REDO) To generate the list of possible scenarios which can happen with a wearable device, we did three things. Firstly, we looked at the most popular list of wearable technologies (including the Fitbit fitness tracker, Pebble smartwatch, and Glass wearable computing device) and their sensors and capabilities. Secondly, we looked at past research in mobile devices and current wearable device considerations. Thirdly, we finished off brainstorming possible things yet to come by looking at vision videos for wearables, and the news for possible concerns.

We already motivated why ubiquitous computing is relevant and we need to do it, so no need to do it here. In the end, we ended up focusing questions on new capabilities that wearables have that smartphones and other devices do not, existing sensors, any concerns which might infringe on security and privacy, along with a couple investigative ones (like if someone recorded all your conversations but never shared it, are you going to be upset? that might be taken out of this paper, but still).

\subsection{Calibrating with Existing Works}
(REDO) Mobile devices threats are well studied and the closest well-researched thing to wearable device threats. We used the same format as Adrienne's paper so that we can compare our results to the ones that she got in her study for mobile devices. We purposed used the same scale and question format as she did in her study, but it's a pretty defensible scale to use anyway and the wording was about consistent with how we were going to do it anyway. Defend the likert scale use and the wording of the question a bit here. Because it is similar, and we also had calibrating questions, we can compare the threats with respect to existing threats studied. We're so relevant, yay.

We used a prompt similar to Fischoff's study so that we could compare our results to the ones that he got in his study, and to put more of the new technologies onto the risk/benefit map. This way, we can have a sense of the risk and benefit with respect to well-studied and more familiar technologies. This also makes the results that we have more accurate and tangible, since people have anchors to base their assessments off of, rather than comparing a bunch of things that seem nebulous to them.

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.  .

\subsection{Methodology}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old. No other restrictions on participation were applier. We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.

>>>>

More formally, a survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables says that most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)\cite{Nilsen}. It is estimated that 20\% the general population owns at least one wearable and 10\% uses at least one wearable in their daily lives \cite{WearableStatNews}. The demographics of wearables consumers are young and rich--48\% of owners are between 18 and 34 years old, and 29\% make over \$100,000 per year. However, it is expected that this \$700 million industry will reach other demographics soon as the prices of wearable devices drop \cite{cmo}.

@@

\subsection{Asking the Right Questions} 
 We asked participants how they would feel if a device shared a particular piece of data with a target recipient. We purposefully asked specific questions limited to the participant, as these situations are easier to judge. The purpose of the bank of ~300 questions was not necessarily to get an absolute ranking of what upsets people and what does not, since the list isn't comprehensive of all possible threats (although top 10 and bottom 10 concerns can be seen in section <linkhere>).The real purpose behind asking an array of questions was to determine how much the device, data type, and data recipient played a role in determining if a person was upset by an event, while also exploring the new threat landscape for wearable devices.

To synthesize the questions, we surveyed popular wearable devices' sensors, studied existing smartphone and wearables literature, and looked at vision videos for wearable devices. In the end, we especially chose  to investigate questions which focused on continuous audio recording, discrete image capture, continuous video capture, and biometrics, due to the prevalence of devices which take voice inputs as commands \cite{StarnerSpeech}, concern for image capture \cite{GlassDetection}, and popularity of fitness tracking \cite{Nilsen}. Exploratory questions, including but not limited to threats regarding information security, pattern recognition, and emotion detection are also studied.

Questions which addressed situations applicable for both smart phone and wearables were deemphasized because these situations had been investigated. However, we did include these questions, primarily to calibrate our results for the other scenarios. We used a seven-point likert scale and used similar wording as Felt in her smartphone study \cite{Felt} so that we could determine both how changing the device in question caused a change in threat perception and how threatening new wearables threats were with respect to existing threats.

\subsection{Looking at the Bigger Picture}

To complement our bank of targeted questions, we also asked participants to assess the comprehensive risks and benefits of a particular technology, over a long period of time, for all parties affected by the technology. The purpose of these questions were not necessarily to get an absolute ranking of technologies by risk or benefit, as perceptions may change (although you can see the rankings in appendix <linkhere>). However, the purpose of these questions was to gain insight into how participants perceived new technologies.

We used a prompt similar to a seminal study in risk perception \cite{Fischhoff} and also asked our participants to rate some of the technologies in the study. We used technologies such as lawnmowers (considered to be low risk and low benefit) and electricity (considered to be low risk and high benefit) as comparison points for other technologies we ask our participants to assess. As a result, we have a mapping of risks and benefits of new technologies with respect to the well-studied technologies.

\subsection{Validation}
We conducted a focus group to validate our survey scope. Of the 13 participants 54\% female, ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist. This time was used to discuss benefits and risks associated with wearables, talk through common concerns, and brainstorm additional scenarios for the survey. The focus group was also used to gauge survey comprehension, user fatigue, and other logistics.

\subsection{Methodology}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old. No other restrictions on participation were applied. We asked questions regarding participants' perceptions of various situations which might occur when wearing a wearable device, and about the risks and benefits of new technologies.
